NAO robot that imitates human movements using Mediapipe\\

### 2024-02-14 Paper/main.tex
[update] paper

\subsection{Computer vision}
% Begin with the computer vision part and the NAOqi API part
In the beginning, the computer vision part was done very easily, because Mediapipe has a lot of usage examples and good documentation. On the other hand working with the NAO robot was a much more difficult.
\\
For the computer vision part we used the opencv library to get images from both camera and videos and then we used the Mediapipe library to get the poses from the images.
We used also the opencv library to plot the landmarks that the Mediapipe library detected, so  we could see how the landmarks were being detected. This landmarks conformed an object with 33 points, which represents landmarks of the human body. (See figure \ref{fig:landmarksMP})

@@

\bibitem{b1} NAOqi API, \textit{http://doc.aldebaran.com/2-5/naoqi/motion/index.html}
\bibitem{b2} Mediapipe Pose Landmarking\textit{https://developers.google.com/mediapipe
/solutions/vision/pose\_landmarker}
\bibitem{b3}I. Irigoyen, "Mimetización de movimiento por robot antropomorfo basado en imágenes de sensor de profundidad," Trabajo Fin de Grado, Facultad de Informática, Grado de Ingeniería Informática, Universidad del País Vasco, 2020.

>>>>

\subsection{Computer vision}
% Begin with the computer vision part and the NAOqi API part
In the beginning, the computer vision part was done very easily, because Mediapipe has a lot of usage examples and good documentation, such as the video "AI Pose Estimation with Python and MediaPipe"\cite{b4}, that helped us a lot on getting the landmarks and calculate some angles. On the other hand working with the NAO robot was a much more difficult, because we did not know how to start.
\\
For the computer vision part we used the opencv library to get images from both camera and videos and then we used the Mediapipe library to get the poses from the images.
We used also the opencv library to plot the landmarks that the Mediapipe library detected, so  we could see how the landmarks were being detected. This landmarks conformed an object with 33 points, which represents landmarks of the human body. (See figure \ref{fig:landmarksMP})

@@

\bibitem{b1} NAOqi API, \textit{http://doc.aldebaran.com/2-5/naoqi/motion/index.html}
\bibitem{b2} Mediapipe Pose Landmarking\textit{https://developers.google.com/mediapipe
/solutions/vision/pose\_landmarker}
\bibitem{b3}I. Irigoyen, "Mimetización de movimiento por robot antropomorfo basado en imágenes de sensor de profundidad," Trabajo Fin de Grado, Facultad de Informática, Grado de Ingeniería Informática, Universidad del País Vasco, 2020.
\bibitem{b4} Nicholas Renotte - Robotics and AI, "AI Pose Estimation with Python and MediaPipe," YouTube, 2021. [Online]. Available: https://www.youtube.com/watch?v=06TE\_U21FK4&t=2109s&ab\_channel=
NicholasRenotte.
